---
title: "R Notebook"
output: html_notebook
---

```{r}
library(rpart)
library(rpart.plot)
library(tidyverse)

titanic_set <- read_csv('data/titanic_decision_tree_data.csv')

shuffle_index <- sample(1:nrow(titanic_set))

# shuffle the data so class order isn't in order - need this for training/testing split later on 
titanic_set <- titanic_set[shuffle_index, ]
```
```{r}
glimpse(titanic_set)
```
```{r}
summary(titanic_set)
```
```{r}
titanic_tidy <- titanic_set %>% 
  select(-X1, -passenger_id, -name, -ticket, -fare, -cabin) %>% 
  drop_na(survived) %>% 
  mutate(sex = as.factor(sex)) %>% 
  mutate(survived = as.factor(survived)) %>% 
  mutate(pclass = as.factor(pclass)) %>% 
  mutate(embarked = as.factor(embarked)) %>% 
  mutate(age_status = ifelse(age <= 16, "child", "adult")) %>% 
  mutate(age_status = as.factor(age_status)) %>% 
  drop_na() %>% 
  select(-age)

summary(titanic_tidy)
```
```{r}
titanic_clean <- titanic_set %>%
  filter(survived %in% c(0,1)) %>%
# Convert to factor level
    mutate(sex = as.factor(sex), 
           age_status = as.factor(if_else(age <= 16, "child", "adult")),
         class = factor(pclass, levels = c(3,2,1), labels = c("Lower", "Middle", "Upper")), 
           survived_flag = factor(survived, levels = c(0,1), labels = c("No", "Yes")), 
           port_embarkation = as.factor(embarked)) %>%
  select(sex, age_status, class, port_embarkation, sib_sp, parch, survived_flag) %>%
  na.omit()
```

```{r}
summary(titanic_clean)
```
```{r}
titanic_clean
```
```{r}
library(GGally)
ggpairs(titanic_clean)
```
Sex, age status, class and port embarked seem to have strong relation in survive prediction. Sibsp and parch does not look to affect much the survived_flag.
```{r}
titanic_clean %>%
  select(survived_flag, sex) %>%
  group_by(survived_flag,sex) %>%
  summarise(total_count = n()) %>%
ggplot() + 
  aes(x = survived_flag, y = total_count, fill = sex) + 
  geom_bar(stat = "identity", position = position_dodge()) + 
  scale_fill_brewer(palette="Dark2") + 
  ylab("total count") + xlab("survived")
```

```{r}
n_data <- nrow(titanic_clean)
```

```{r}
test_index <- sample(1:n_data, size = n_data * 0.2)
```
```{r}
titanic_test  <- slice(titanic_clean, test_index)
titanic_train <- slice(titanic_clean, -test_index)
```
I chose usual split which is 80:20 for this analysis.
```{r}
titanic_test %>% 
  janitor::tabyl(survived_flag)
```
```{r}
titanic_train %>% 
  janitor::tabyl(survived_flag)
```
```{r}
titanic_fit <- rpart(
  formula = survived_flag ~ .,
  data = titanic_train,
  method = "class"
)
```

```{r}
rpart.plot(titanic_fit, yesno = 2, fallen.leaves = TRUE, faclen = 6, digits = 4)

```
Around 40% of all people in data has not survived and if you are male you have 65% to not survive. The higher chances to survive if you are female and from higher class (22%). But if you are female from lower class then there are 13 chances to not survive. If you have siblings more than 1 then there are less chances to survive (8%).
```{r}
library(modelr)

titanic_test_pred <- titanic_test %>% 
  add_predictions(titanic_fit, type = "class")

titanic_test_pred
```
```{r}
library(yardstick)
```
```{r}
conf_mat <- titanic_test_pred %>% 
  conf_mat(truth = survived_flag, estimate = pred)

conf_mat
```
```{r}
accuracy <- titanic_test_pred %>% 
  accuracy(truth = survived_flag, estimate = pred)

accuracy
```
it has around 76% accuracy based on test data which is quite good. Diagonal from top left to bottom right shows true positives and true negatives.
```{r}
titanic_fit <- rpart(
  formula = survived_flag ~ .,
  data = titanic_train,
  method = "class",
  control = rpart.control(maxdepth = 20, xval = 5, cp = 0)
)

rpart.plot(titanic_fit, yesno = 2, fallen.leaves = TRUE, faclen = 6, digits = 4, type = 4, extra = 101)
```

