---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
inmates_data <- read_tsv("data/inmates.tsv")
```
## Change the ‘M’/‘F’ values in gender to be ‘Male’/‘Female’.
```{r}
inmates_data %>% 
  mutate(gender = case_when(gender == "M" ~ "Male",
                            gender == "F" ~ "Female"))
```
```{r}
inmates_data %>% 
  mutate(gender = if_else(gender == 'M', 'Male', 'Female'))

```

## For the race variable, everything is in capital letters, change each level to title case. Also combine ‘AMER IND’ and ‘ASIAN’ into an ‘Other’ category.
```{r}
inmates_data  %>% 
  mutate(race = str_to_title(race)) %>% 
  mutate(race = recode(race, "Amer Ind" = "Other",
                       "Asian" = "Other"))
```
## Make a new variable bond_level which is High whenever the bond for an inmate is above $1,000,000 and Normal otherwise.
```{r}
bond_level_data <- inmates_data %>% 
  mutate(bond_level = case_when(bond_amount > 1000000 ~ "High",
                                 TRUE ~ "Normal"))
bond_level_data
```
## How many inmates have a high bond level?
```{r}
bond_level_data %>% 
  filter(bond_level == "High") %>% 
  summarise(total = n())
```
## Modify the detainer variable so that NONE, IMIGRATION and FEDERAL are in title case and all other levels are set to Other.
```{r}
bond_level_data %>% 
  mutate(detainer = str_to_title(detainer)) %>% 
  mutate(detainer = recode(detainer, "Other State" = "Other",
                           "Special Parole" = "Other",
                           "State Of Ct" = "Other",
                           "Do Not Release" = "Other"))
```


