---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```
```{r}
salaries <- read_csv("data/salaries.csv")
```
```{r}
head(salaries)
```
Q1:
```{r}
salaries %>% 
  select(beginning_salary, current_salary)
```

Q2: 
```{r}
salaries %>% 
  filter(age > 50 & current_salary > 20000)
```
Q3:
```{r}
salaries %>% 
  arrange(desc(current_salary))
```
Q4:
```{r}
salaries %>% 
  mutate(beginning_salary_pence = beginning_salary * 100, 
         current_salary_pence = current_salary * 100)
```
Q5:
```{r}
salaries %>% 
  summarise(max(age), min(age))
```

Q6:
```{r}
salaries %>% 
  summarise(max(current_salary), min(current_salary))
```
Q7:
```{r}
salaries %>% 
  filter(age < 30)
```

Q8:

```{r}
arrange(salaries, educational_level, age)
```
Q9:
```{r}
salaries %>% 
  select(is.numeric)

```
Q10:
```{r}
salaries %>% 
  filter(work_experience < 2 | educational_level < 12)
```
Q11:
```{r}
salaries %>% 
  summarise(current_salary/1000, beginning_salary/1000)
  
```
Q12:
```{r}
salaries %>% 
  filter(gender == "female", employment_category == "security officer")
```
Number 2.
Q1:
```{r}
salaries %>% 
  group_by(educational_level) %>% 
  summarise(average = mean(current_salary)) %>% 
  filter(educational_level <= 16) %>% 
  arrange(desc(average))
```
Q2:
```{r}
salaries %>%
  filter(work_experience > 2) %>%
  group_by(gender, employment_category) %>%
  summarise(mean_salary = mean(current_salary))
```
Q3:
```{r}
salaries %>% 
  group_by(employment_category) %>% 
  summarise(dif = mean(current_salary) - median(current_salary)) %>% 
  arrange(desc(dif))
```
Number 3:

```{r}
beer <- read.delim("data/beer.txt", sep = ";", dec = ".")
beer
```
Q1:
```{r}
beer %>% 
  filter(is.na(carbohydrates))
```
Q2:
```{r}
beer %>% 
  filter(is.na(brand))
```
Q3:
If brand is missing then most of the data is missed. 
We have less values missing for the brand variable. Most of the observations that are missing brand are also missing all other observations. This means it might be quite sensible to drop the rows where brand is missing. If would be less sensible to drop the observations that are missing carbohydrates as we still have a lot of useful information in those rows. However, in same cases (like a specific study of carbohydrates in beer) we might want to only include rows with carbohydrate data. 
```{r}
beer %>% 
  drop_na(carbohydrates, brand)
```
Number 4:
```{r}
inmates <- read_tsv("data/inmates.tsv")
inmates
```
Q1:
```{r}
inmates <- mutate(inmates, gender = if_else(gender == 'M', 'Male', 'Female'))

inmates %>% 
  select(gender) %>% 
  mutate(gender = recode(gender, "M" = "Male", "F" = "Female"))
```
Q2:
```{r}
inmates %>% 
  select(race) %>% 
  mutate(race = recode(race, "WHITE" = "White", 
                       "BLACK" = "Black", 
                       "HISPANIC" = "Hispanic", .default = "Other"))
```
Q3:
```{r}
inmates <- mutate(inmates, bond_level = if_else(bond_amount > 1000000, 'High', 'Normal'))
inmates
```

```{r}
bond_inmates <- inmates %>% 
  mutate(bond_level = case_when(
    bond_amount > 1000000 ~ "High",
    TRUE ~ "Normal"
  ))

bond_inmates
```
```{r}
bond_inmates %>% 
  filter(bond_level == "High") %>% 
  count()
```
```{r}
inmates %>% 
  mutate(detainer = recode(detainer,
    "NONE" = "None",
    "IMIGRATION" = "Imigration",
    "FEDERAL" = "Federal", .default = "Other"))
```






