---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
movies <- read_csv("data/movies.csv")
```

```{r}
head(movies)
```
```{r}
dim(movies)
```
Q1: 
* Original title and title looks the same so I would remove one of the column.
*I don't think I need homepage, overview and tagline so I would remove these columns.
*I would put all the title to lower case.
*I would remove all NAs.
*I would use clean_names function from janitor.

there seems to be a lot of NAs in the homepage and tagline columns
there are two columns: original_title and title that seem to contain similar things
there’s a lot of movies with a budget and revenue of 0 - presumably missing data
you’d lose 3310 out of 4803 rows if you dropped all NAs - that’s a bit much, so probably better to deal with them in some other way

```{r}
movies_selected <- movies %>% 
  select(original_title, runtime, budget)

movies_selected
```

```{r}
movies_selected %>% 
  summarise(sum_of_NA = sum(is.na(original_title), is.na(runtime), is.na(budget)))
```


```{r}
sum(is.na(movies_selected))
```


```{r}
movies_runtime <- movies_selected %>%
  mutate(runtime = na_if(runtime, 0))  %>% 
  summarise(count = sum(is.na(runtime)))
  
movies_runtime
```
```{r}
sum(is.na(movies_runtime))

```
```{r}
movies_selected %>% 
  summarise(across(.fns = ~sum(is.na(.x))))
```

Impute the missing values in runtime with the median runtime using coalesce and save this into a new variable called movies_imputed. There should now be no missing values in the column runtime - check this to make sure.

```{r}
movies_imputed <- movies_runtime %>% 
  mutate(runtime = coalesce(runtime, median(runtime, na.rm = TRUE)))

movies_imputed
```

```{r}
sum(is.na(movies_imputed))
```
```{r}
longest_runtime <- movies_imputed %>% 
  slice_max(runtime, n = 10)

longest_runtime
```
```{r}
shortest_runtime <- movies_imputed %>% 
  slice_min(runtime, n = 10)

shortest_runtime
```


```{r}
md <- median(movies_imputed$budget)
movies_imputed <- movies_imputed %>% 
  mutate(budget = 
           if_else(budget < 100, md, budget))

new_budget
```

Extension
```{r}
movie_budgets <- movies_imputed %>%
  mutate(
    budget_type = case_when(
      budget < 12e6 ~ "Small budget",
      budget < 40e6 ~ "Medium budget",
      budget >= 40e6 ~ "Big budget"
      )
    )

movie_budgets

```

```{r}
str(movies)
```
```{r}
movies %>% 
  summarise(across(where(is.numeric), ~sum(is.na(.x)))) 



```

```{r}
movies %>%
  summarise(across(where(is.character), ~sum(is.na(.x))))
```
```{r}
movies_selected %>% 
  summarise(across(.fns = ~sum(is.na(.x))))
```


