---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```
```{r}
house <- read_csv("data/kc_house_data.csv")
house
```
```{r}
house_tidy <- house %>% 
  select(-c(id, date, sqft_living15, sqft_lot15, zipcode)) %>% 
  mutate(waterfront = as.logical(waterfront)) %>% 
  mutate(renovated = ifelse(yr_renovated > 0, TRUE, FALSE)) %>% 
  select(-yr_renovated)  %>%
  mutate(condition = as_factor(condition)) %>%
  mutate(grade = as_factor(grade))

house_tidy
```
Check for aliased variables using the alias() function (this takes in a formula object and a data set). [Hint - formula price ~ . says ‘price varying with all predictors’, this is a suitable input to alias()]. Remove variables that lead to an alias. Check the ‘Elements of multiple regression’ lesson for a dropdown containing further information on finding aliased variables in a dataset.
```{r}
alias(price ~., house_tidy)

house_data <- house_tidy %>% 
  select(-sqft_living)
```
```{r}
alias(price ~., house_data)
```
```{r}
library(GGally)
```
```{r}
houses_tidy_numeric <- house_data %>%
  select_if(is.numeric)

houses_tidy_nonnumeric <- house_data %>%
  select_if(function(x) !is.numeric(x))

houses_tidy_nonnumeric$price <- house_data$price

ggpairs(houses_tidy_numeric, progress = FALSE)
ggpairs(houses_tidy_nonnumeric, progress = FALSE)
```
```{r}
model1 <- lm(price ~ grade, data = house_data)
summary(model1)

par(mfrow = c(2,2))
plot(model1)
```
```{r}
null_model <- lm(price ~ 1, data = house_data)
grade_model <- lm(price ~ grade, data = house_data)
anova(null_model, grade_model)
```

```{r}
library(modelr)
price_remaining_resid <- house_data %>% 
  add_residuals(model1) %>% 
  select(-c(price, grade))

houses_resid_numeric <- price_remaining_resid %>%
  select_if(is.numeric)

houses_resid_nonnumeric <- price_remaining_resid %>%
  select_if(function(x) !is.numeric(x))

houses_resid_nonnumeric$resid <- price_remaining_resid$resid
```

```{r}
houses_resid_nonnumeric %>% 
  ggpairs(aes( alpha = 0.5), progress = FALSE)

houses_resid_numeric %>% 
  ggpairs(aes( alpha = 0.5), progress = FALSE)

```
```{r}
model2 <- lm(price ~ grade + lat, data = house_data)
summary(model2)

par(mfrow = c(2,2))
plot(model2)
```
```{r}
price_remaining_resid <- house_data%>% 
  add_residuals(model2) %>% 
  select(-c(price, grade, lat))

houses_resid_numeric <- price_remaining_resid %>%
  select_if(is.numeric)

houses_resid_nonnumeric <- price_remaining_resid %>%
  select_if(function(x) !is.numeric(x))

houses_resid_nonnumeric$resid <- price_remaining_resid$resid
```

```{r}
houses_resid_nonnumeric %>% 
  ggpairs(aes( alpha = 0.5), progress = FALSE)

houses_resid_numeric %>% 
  ggpairs(aes( alpha = 0.5), progress = FALSE)
```

```{r}
model3 <- lm(price ~ grade + lat + view, data = house_data)
summary(model3)

par(mfrow = c(2,2))
plot(model3)
```
```{r}
anova(model2, model3)
```
```{r}
price_remaining_resid <- house_data %>% 
  add_residuals(model3) %>% 
  select(-c(price, grade, lat, view))

houses_resid_numeric <- price_remaining_resid %>%
  select_if(is.numeric)

houses_resid_nonnumeric <- price_remaining_resid %>%
  select_if(function(x) !is.numeric(x))

houses_resid_nonnumeric$resid <- price_remaining_resid$resid
```

```{r}
houses_resid_nonnumeric %>% 
  ggpairs(aes( alpha = 0.5), progress = FALSE)

houses_resid_numeric %>% 
  ggpairs(aes( alpha = 0.5), progress = FALSE)
```
```{r}
price_resid <- house_data %>% 
  add_residuals(model3) %>% 
  select(-price)

price_resid %>% 
  ggplot(aes(x = view, y = resid, color = grade)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```
```{r}
price_resid %>% 
  ggplot(aes(x = sqft_basement, y = resid, color = grade)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```
```{r}
model4 <- lm(price ~ grade + lat + view + sqft_basement + view:sqft_basement, data = house_data)
summary(model4)

par(mfrow = c(2,2))
plot(model4)
```
```{r}
model5 <- lm(price ~ grade + lat + view + sqft_basement + lat:sqft_basement, data = house_data)
summary(model5)

par(mfrow = c(2,2))
plot(model5)
```
```{r}
library(relaimpo)
calc.relimp(model4, type = "lmg", rela = TRUE)
```
```{r}
price_resid %>%
  ggplot(aes(x = sqft_basement, y = resid, colour = grade)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~ grade)
```



