---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```
```{r}
house <- read_csv("data/kc_house_data.csv")
house
```
```{r}
house_tidy <- house %>% 
  select(-c(id, date, sqft_living15, sqft_lot15, zipcode)) %>% 
  mutate(waterfront = as.logical(waterfront)) %>% 
  mutate(renovated = ifelse(yr_renovated > 0, TRUE, FALSE)) %>% 
  select(-yr_renovated)

house_tidy
```
Check for aliased variables using the alias() function (this takes in a formula object and a data set). [Hint - formula price ~ . says ‘price varying with all predictors’, this is a suitable input to alias()]. Remove variables that lead to an alias. Check the ‘Elements of multiple regression’ lesson for a dropdown containing further information on finding aliased variables in a dataset.
```{r}
alias(price ~., house_tidy)

house_data <- house_tidy %>% 
  select(-c(sqft_living, sqft_above, sqft_basement))
```
```{r}
summary(house_data)
```
```{r}
library(GGally)

house_data %>% 
  ggpairs(aes(colour = renovated, alpha = 0.5))
```
```{r}
houses_tidy_numeric <- house_data %>%
  select_if(is.numeric)

houses_tidy_nonnumeric <- house_data %>%
  select_if(function(x) !is.numeric(x))

houses_tidy_nonnumeric$price <- house_data$price

ggpairs(houses_tidy_numeric)
ggpairs(houses_tidy_nonnumeric)
```
```{r}
model1 <- lm(price ~ grade, data = houses_tidy_numeric)
summary(model1)

par(mfrow = c(2,2))
plot(model1)
```
```{r}
library(modelr)
price_remaining_resid <- houses_tidy_numeric %>% 
  add_residuals(model1) %>% 
  select(-c(price, grade))
```

```{r}
price_remaining_resid %>% 
  ggpairs(aes( alpha = 0.5))
```
```{r}
model2 <- lm(price ~ grade + bathrooms, data = houses_tidy_numeric)
summary(model2)

par(mfrow = c(2,2))
plot(model2)
```
```{r}
price_remaining_resid <- houses_tidy_numeric %>% 
  add_residuals(model2) %>% 
  select(-c(price, grade, bathrooms))
```

```{r}
price_remaining_resid %>% 
  ggpairs(aes( alpha = 0.5))
```

```{r}
house_data %>% 
  select(price, grade, bathrooms, waterfront, renovated) %>% 
  ggpairs()
```

```{r}
model3 <- lm(price ~ grade + bathrooms+ renovated, data = house_data)
summary(model3)

par(mfrow = c(2,2))
plot(model3)
```
```{r}
anova(model2, model3)
```
```{r}
price_remaining_resid <- house_data %>% 
  add_residuals(model3) %>% 
  select(-c(price, grade, bathrooms, renovated))
```

```{r}
price_remaining_resid %>% 
  ggpairs(aes( alpha = 0.5))
```


