---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(scales)
library(CodeClanData)
```
```{r}
qb_revenue_breakdown
qb_monthly_sales
qb_competitors
qb_device_data
```
Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.
```{r}
ggplot(qb_revenue_breakdown) +
  aes(x = Year, y = Revenue, fill = Product) +
  geom_col() +
  labs(title = "Sources of revenue in 2018 and 2019") +
  theme_light()+
  theme(title = element_text(size = 12))+
  scale_fill_manual(values = c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040"))
```
Make a line chart showing monthly sales of the “flagship product” - the KwikBit Unit1 - over the last year. This data is inside qb_monthly_sales, but you will need to use subset.
```{r}
ggplot(qb_monthly_sales) +
  aes(x = Date, y = Amount, color = Cashflow) +
  geom_line(data = subset(qb_monthly_sales, Cashflow %in% "Kwikbit Unit 1 Sales")) +
  labs(title = "KwikBit amount over two years") +
  scale_y_continuous(limits = c(0,630)) +
  theme_light()+
  theme(title = element_text(size = 12))+
  scale_color_manual(values = c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040"), guide = "none")
```
Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales.
```{r}
ggplot(qb_monthly_sales) +
  aes(x = Date, y = Amount, color = Cashflow) +
  geom_line(data = subset(qb_monthly_sales, Cashflow %in% c("Total Revenue", "Cost"))) +
  labs(title = "Cost and revenue amount over two years") +
  scale_y_continuous(limits = c(0,3000)) +
  theme_light()+
  theme(title = element_text(size = 12))+
  scale_color_manual(values = c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040"))
```
Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors.
```{r}
ggplot(qb_competitors) +
  aes(x = Year, y = Revenue, fill = Company) +
  geom_area() +
  labs(title = "Revenue of 4 competitors over 4 years") +
  theme_light() +
  theme(title = element_text(size = 12))+
  scale_fill_manual(values = c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")) +
  scale_y_continuous(labels = comma)
```
```{r}
ggplot(qb_competitors) +
  aes(x = Year, y = Revenue, fill = Company) +
  geom_col(position = "dodge") +
  labs(title = "Revenue of 4 competitors over 4 years") +
  theme_light() +
  theme(title = element_text(size = 12))+
  scale_fill_manual(values = c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")) +
  scale_y_continuous(labels = comma)
```

Now show the sales from the 5 competitors as a line graph. Include an extra layer that shows the data points used to make the lines.
```{r}
ggplot(qb_competitors) +
  aes(x = Year, y = Revenue, color = Company, fill = Company) +
  geom_line() +
  geom_point() +
  labs(title = "Revenue of 4 competitors over 4 years") +
  theme_light() +
  theme(title = element_text(size = 12))+
  scale_color_manual(values = c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040"))
```
Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between individuals and people. Data is in qb_device_data.
```{r}

qb_device_data_time <- qb_device_data %>% 
  mutate(time = hours * 60 + mins)

ggplot(qb_device_data_time) +
  aes(x = time, y = counts, color = device) +
  geom_line() +
  facet_grid(id~ device) +
  labs(x = "Time (mins)",
       y = "Counts",
       title = "Counts between company and competitors over time") +
  theme_light() +
  theme(title = element_text(size = 12)) +
  scale_color_manual(values = c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040"))
```
```{r}
theme_qb <- 
  theme(
    text = element_text(size = 12),
    title = element_text(size = 14),
    axis.text = element_text(size = 10),
    panel.background = element_rect(fill = "white"),
    panel.grid = element_line(colour = "grey90", linetype = "dashed")
  )

col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")
```
```{r}
revenue_and_costs <- subset(qb_monthly_sales, Cashflow != "Kwikbit Unit 1 Sales")

ggplot(revenue_and_costs) +
  aes(x = Date, y = Amount, colour = Cashflow, group = Cashflow) +
  geom_line(size = 2) +
  theme_qb +
  scale_colour_manual(values = col_scheme) +
  scale_y_continuous("Sales", labels = scales::dollar_format(prefix = "£")) +
  ggtitle("QikBit - Revenue and Costs", subtitle = "1 Aug 2018 to 1 July 2019")
```
```{r}
ggplot(qb_competitors) +
  aes(x = Year, y = Revenue, colour = Company) +
  geom_line() +
  geom_point() +
  scale_y_continuous(labels = scales::dollar) +
  theme_qb +
  scale_colour_manual(values = col_scheme) +
  ggtitle(
    "Revenue in the Fitness Tracker Market by Company",
    subtitle = "2015 - 2019"
  )
```



