---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
books <- read_csv("data/books.csv")
books
```

```{r}
glimpse(books)
```
```{r}
sum(is.na(books))
```
Remove all na.
```{r}
books <- na.exclude(books)
```
```{r}
names(books)
```

Find the best authors.
```{r}
best_authors <- books %>% 
  select(authors, average_rating) %>% 
  group_by(authors) %>% 
  summarise(best = median(average_rating)) %>% 
  arrange(desc(best)) %>% 
  head(n = 100)
  
best_authors
```
Find the most popular publisher.
```{r}
best_publisher <- books %>% 
  select(publisher, average_rating) %>% 
  group_by(publisher) %>% 
  summarise(best_p = median(average_rating)) %>% 
  arrange(desc(best_p))

best_publisher
```
Calculate which publisher has the most books.
```{r}
most_books <- books %>% 
  select(publisher, bookID) %>% 
  group_by(publisher) %>% 
  mutate(total = bookID - bookID + 1) %>% 
  count(total) %>% 
  arrange(desc(n))
  
most_books

```
```{r}
unique(books$language_code)
```
```{r}
books_language <- books %>% 
  select(language_code, bookID) %>% 
  mutate(language_code = recode(language_code, "en-GB" = "eng", "en-CA" = "eng",
                                "en-US" = "eng"))
```
Most frequent language used.
```{r}
books_language %>% 
  select(language_code, bookID) %>% 
  group_by(language_code) %>% 
  mutate(total_l = bookID - sbookID + 1) %>% 
  count(total_l) %>% 
  arrange(desc(n))

```
The latest publication date.
```{r}
books %>% 
  select(publication_date) %>% 
  slice_max(publication_date)
```
The latest publication date.
```{r}
books %>% 
  select(publication_date) %>% 
  slice_min(publication_date)
```
Find the best book (title). 

```{r}
best_book <- books %>% 
  select(title, average_rating) %>% 
  group_by(title) %>% 
  summarise(best = median(average_rating)) %>% 
  arrange(desc(best)) %>% 
  head(n = 100)
  
best_book
```
Books with the most ratings count.
```{r}
books %>% 
  select(title, ratings_count) %>% 
  arrange(desc(ratings_count))
```
```{r}
books %>% 
  select(title, text_reviews_count) %>% 
  arrange(desc(text_reviews_count))
```
```{r}
books %>% 
  select(bookID, title) %>% 
  sample_n(1)
```

```{r}
books <- books %>%
  mutate(
    language = recode(language_code,
                  “eng” = “English”,
                  “en-US” = “English (United States)“,
                  “en-GB” = “English (United Kingdom”,
                  “en-CA” = “English (Canada)“,
                  “fre” = “French”,
                  “spa” = “Spanish”,
                  “mul” = “Multiple Languages”,
                  “grc” = “Ancient Greek”,
                  “enm” = “Middle English”,
                  “ger” = “German”,
                  “jpn” = “Japanese”,
                  “ara” = “Arabic”,
                  “nl” = “Dutch”,
                  “zho” = “Chinese”,
                  “lat” = “Latin”,
                  “por” = “Portuguese”,
                  “srp” = “Serbian”,
                  “ita” = “Italian”,
                  “glg” = “Galician”,
                  “wel” = “Welsh”,
                  “swe” = “Swedish”,
                  “nor” = “Norwegian”,
                  .default = “Other Language”)
)
