---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
```

```{r}
mobile <- read_csv("data/20190928-items.csv") %>% clean_names()

names(mobile)
glimpse(mobile)
dim(mobile)
```
Find the brand with the highest numbers of phones in the dataset.
```{r}
mobile %>% 
  group_by(brand) %>% 
  summarise(total = n()) %>% 
  arrange(desc(total)) %>% 
  head(1)
```
For your top brand, plot the distribution of phone ratings as a probability density, overlaying a fitted normal distribution. Do you think the normal distribution provides a good model of these ratings?
```{r}
samsung_stats <- mobile %>% 
  filter(brand == "Samsung") %>% 
  summarise(
    num = n(),
    mean = mean(rating),
    sd = sd(rating)
  )

samsung_stats
```
```{r}
samsung_stats_fitdistr <- MASS::fitdistr(x = samsung_ratings$rating, densfun = "normal")
samsung_stats_fitdistr
```

```{r}
mobile %>% 
  filter(brand == "Samsung") %>% 
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = ..density..), col = "white", bins = 25) +
  stat_function(
    fun = dnorm,
    args = list(
      mean = samsung_stats$mean,
      sd = samsung_stats$sd
    ), 
    col = "red"
  )
```
The graph is skewed to left so it does not provide a good model of these ratings.

It’s a reasonable fit: the distribution is roughly bell-shaped. The main problems seem to be a larger number of ratings in the tails of the distribution than are predicted by the normal, at ratings 1
, 2
 and 5

We can be more quantitative in comparing the distribution of top brand ratings with a normal distribution. You calculated the mean() and sd() of your distribution in an earlier question. Use these values to calculate the proportions of ratings within one-, two- and three standard deviations of the mean. Compare these proportions with those you expect for a normal distribution.
```{r}
samsung_ratings <- mobile %>%
  select(brand, rating) %>% 
  filter(brand == "Samsung")
```

```{r}
mobile %>%
  select(brand, rating) %>% 
  filter(brand == "Samsung") %>% 
  filter(rating >= samsung_stats$mean - samsung_stats$sd) %>%
  filter(rating <= samsung_stats$mean + samsung_stats$sd) %>%
  summarise(prop_within_1sd = n() / nrow(samsung_ratings))
```
```{r}
mobile %>%
  select(brand, rating) %>% 
  filter(brand == "Samsung") %>% 
  filter(rating >= samsung_stats$mean - 2 *samsung_stats$sd)%>%
  filter(rating <= samsung_stats$mean + 2* samsung_stats$sd) %>%
  summarise(prop_within_2sd = n() / nrow(samsung_ratings))
```

```{r}
mobile %>%
  select(brand, rating) %>% 
  filter(brand == "Samsung") %>% 
  filter(rating >= samsung_stats$mean - 3* samsung_stats$sd) %>%
  filter(rating <= samsung_stats$mean + 3* samsung_stats$sd) %>%
  summarise(prop_within_3sd = n() / nrow(samsung_ratings))
```
After 3 sd it does not even cover half of rating which means that data is skewed 
and there are outliers and distribution is not uniform.

For a normal distribution, expect 68%
 of values to fall within one standard deviation of the mean. Here, 79%
 of ratings are within this range, so our distribution is slightly too central.

Adding another standard deviation to either side should increase the proportion of values by 27%
 to 95%
 overall in a normal distribution. Our distribution adds 13%
, going to 92%
 overall, so there are too few values in the range from one- to two standard deviations.

Finally, in a normal distribution, adding a further standard deviation to either side should increase the proportion of values by 4.7%
 to 99.7%
 overall. Our distribution adds 6%
 to 98%
, so this is pretty close.
```{r}
qq <- mobile %>% 
  filter(brand == "Samsung")

qqnorm(qq$rating, pch = 1, frame = FALSE)
qqline(qq$rating, col = "steelblue", lwd = 2)
```
Here we see significant deviations from straight line in the tails, so the data is not very well approximated as normal.



