---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```
```{r}
customers <- read_csv("mall_customers.csv") %>% janitor::clean_names()
customers
```
```{r}
customers %>%
  group_by(gender) %>%
  summarise(count = n()) %>%
ggplot(aes(x = gender, y = count)) +
  geom_col()
```

```{r}
customers %>% 
  ggplot(aes(x = annual_income_k, y = spending_score_1_100, colour = gender)) +
  geom_point()
```
```{r}
customers %>% 
  ggplot(aes(x = age, y = spending_score_1_100, colour = gender)) +
  geom_point()
```
There is difference in groups between age but not much difference between gender.
```{r}
customers_tidy <- customers %>% 
  mutate_if(is.numeric, scale) %>% 
  select(-customer_id, -gender, -age)

customers_tidy
```
```{r}
max_k <- 20 

k_clusters <- tibble(k = 2:max_k) %>%
  mutate(
    kclust = map(k, ~ kmeans(customers_tidy, .x, nstart = 25)), 
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, customers_tidy)
  )

k_clusters
```

```{r}
clustered_customers <- kmeans(customers_tidy, centers = 6, nstart = 25)
clustered_customers
```
```{r}
library(broom)
glance(clustered_customers)
```
```{r}
augment(clustered_customers, customers_tidy) %>% 
  ggplot(aes(x = annual_income_k, y = spending_score_1_100, colour = .cluster)) +
  geom_point() 
```
There are definitely 5 clusters noticed by eye.
```{r}
library(factoextra)
fviz_nbclust(customers_tidy, kmeans, method = "wss", nstart = 25)
```
```{r}
fviz_nbclust(customers_tidy, kmeans, method = "silhouette", nstart = 25)

```
```{r}
fviz_nbclust(customers_tidy, kmeans, method = "gap_stat", k.max = 10)
```
Elbow method has shown value at around 4 and 5, the 2nd method shows number 5 and the last method shows number 1. For the next clustering, 5 k will be used. 
```{r}
clustered_customers <- kmeans(customers_tidy, centers = 5, nstart = 25)
clustered_customers
```
```{r}
augment(clustered_customers, customers_tidy) %>% 
  ggplot(aes(x = annual_income_k, y = spending_score_1_100, colour = .cluster)) +
  geom_point() 
```
There are definite 5 clusters of people according to annual income and spending score and it seems like a good fit for the data.
People can be segmented into 5 groups:
1) low income, low spend 
2) high income, low spend 
3) high income, high spend
4) low income, high spend
5) moderate income and spend


